### 2018-01-21 Chapters/Chapter01.tex
Update on Overleaf.

Many exchanges require at least six confirmations in order to accept a deposit in Bitcoin. So, for $n=6$, $\mathbf{P}(Y_6 < 1 \text{ hour}) = \mathbf{P}(Y_6 < 3600) = 0.5543$. The symmetrical confidence interval with $\alpha=10\%$ is $[27, 105]$ in minutes. Thus, 90\% of the times, it will take between 27 minutes and 1 hour and 45 minutes to have your deposit accepted --- assuming that your transaction will be confirmed in the very next block.

>>>>

Many exchanges require at least six confirmations in order to accept a deposit in Bitcoin. So, for $n=6$, $\mathbf{P}(Y_6 < 1 \text{ hour}) = \mathbf{P}(Y_6 < 3600) = 0.5543$. The symmetrical confidence interval with $\alpha=10\%$ is $[27, 105]$ in minutes. Thus, 90\% of the times, it will take between 27 minutes and 1 hour and 45 minutes to have your deposit accepted --- assuming that your transaction will be confirmed in the very next block. The pdf of $Y_6$ is shown in Figure \ref{fig-bitcoin-time-6-blocks}. The 10\% symmetrical confidence interval is shown in the white area.

\begin{figure}[ht]
\centering\includegraphics[height=5cm]{./images01/time-6-blocks.pdf}
\caption{Probability density function of $Y_6$, i.e., probability of finding 6 blocks after time $t$. The shaded areas shows the lower 5\% and upper 5\% of the pdf.\label{fig-bitcoin-time-6-blocks}}
\end{figure}
